dissemr
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.org/ropenscilabs/dissemr.svg?branch=master)](https://travis-ci.org/ropenscilabs/dissemr)
[![codecov.io](https://codecov.io/github/ropenscilabs/dissemr/coverage.svg?branch=master)](https://codecov.io/github/ropenscilabs/dissemr?branch=master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/dissemr)](https://github.com/metacran/cranlogs.app)

[dissem.in](https://dissem.in/) client

API docs: <https://dev.dissem.in/api.html>

## Install

Development version

```{r eval=FALSE}
devtools::install_github("ropenscilabs/dissemr")
```

```{r}
library("dissemr")
```

## single DOI

```{r}
diss_dois("10.1016/j.paid.2009.02.013")
```

## many DOIs

```{r}
diss_dois(c("10.1016/j.paid.2009.02.013", "10.1186/s40687-015-0044-7"))
```

## search

```{r}
(res <- diss_search(query = "cellular biology"))
```

dig into individual results

```{r}
res$papers[1:2]
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/dissemr/issues).
* License: MIT
* Get citation information for `dissemr` in R doing `citation(package = 'dissemr')`
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
